\documentclass[review]{elsarticle}

\usepackage{lineno,hyperref}
\modulolinenumbers[5]

% Package to change into landscape
\usepackage{pdflscape}

% Package for table
\usepackage{booktabs}

% For some math expression
\usepackage{amsmath}
\usepackage{mathabx}
\DeclareMathOperator*{\argmin}{arg\,min}

% Package for SI units
\usepackage{siunitx}

% Package for figures
\usepackage{epsf,graphicx}
\usepackage{epstopdf}
\usepackage{subfigure}

% Package for pseudo algorithm
\usepackage{algorithm}
\usepackage[noend]{algpseudocode}
\makeatletter
\def\BState{\State\hskip-\ALG@thistlm}
\makeatother

% Define the operator of convolution
\newcommand{\Conv}{\mathop{\scalebox{1.5}{\raisebox{-0.2ex}{$\ast$}}}}%

% Use the acro package to handle the acronym
\usepackage{acro}
\input{00_files_system/acro_def.tex}

\journal{Medical Image Analysis}

%%%%%%%%%%%%%%%%%%%%%%%
%% Elsevier bibliography styles
%%%%%%%%%%%%%%%%%%%%%%%
%% To change the style, put a % in front of the second line of the current style and
%% remove the % from the second line of the style you would like to use.
%%%%%%%%%%%%%%%%%%%%%%%

%% Numbered
%\bibliographystyle{00_files_system/model1-num-names}

%% Numbered without titles
%\bibliographystyle{00_files_system/model1a-num-names}

%% Harvard
\bibliographystyle{00_files_system/model2-names}\biboptions{authoryear}

%% Vancouver numbered
%\usepackage{00_files_system/numcompress}\bibliographystyle{00_files_system/model3-num-names}

%% Vancouver name/year
%\usepackage{numcompress}\bibliographystyle{00_files_system/model4-names}\biboptions{authoryear}

%% APA style
%\bibliographystyle{00_files_system/model5-names}\biboptions{authoryear}

%% AMA style
%\usepackage{numcompress}\bibliographystyle{00_files_system/model6-num-names}

%% `Elsevier LaTeX' style
%\bibliographystyle{elsarticle-num}
%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

\begin{frontmatter}

\title{Automatic prostate cancer detection through \acs*{dce}-\acs*{mri} images: all you need is a good normalization}

% Add authors and the different addresses
\author[label1,label3]{Guillaume~Lema\^itre\corref{cor1}}
\ead{g.lemaitre58@gmail.com}
\author[label3]{Robert~Mart\'i}
\author[label1]{Mojdeh~Rastgoo}
\author[label1]{Joan~Massich}
%\ead{marly@eia.udg.edu}
\author[label3]{Jordi~Freixenet}
%\ead{jordif@eia.udg.edu}
\author[label5]{Anke Meyer-Baese}
%\ead{ameyerbaese@fsu.edu}
\author[label4]{Joan~C.~Vilanova}
%\ead{kvilanova@comg.cat}
%\author[label2]{Paul~M.~Walker}
%\ead{pwalker@u-bourgogne.fr}
\author[label1,label6]{Fabrice~Meriaudeau}
%\ead{fabrice.meriaudeau@u-bourgogne.fr}
\address[label1]{\scriptsize LE2I UMR6306, CNRS, Arts et M\'etiers, Univ. Bourgogne Franche-Comt\'e, 12 rue de la Fonderie, 71200 Le Creusot, France}
%\address[label2]{\scriptsize LE2I UMR6306, CNRS, Arts et M\'etiers, Univ. Bourgogne Franche-Comt\'e, Avenue Alain Savary, 21000 Dijon, France}
\address[label3]{\scriptsize ViCOROB, Universitat de Girona, Campus Montilivi, Edifici P4, 17071 Girona, Spain}
\address[label4]{\scriptsize Department of Magnetic Resonance, Cl\'inica Girona, Lorenzana 36, 17002 Girona, Spain}
\address[label5]{\scriptsize Department of Scientific Computing, 400 Dirac Science Library, Florida State University, Tallahassee, FL 32306, United States}
\address[label6]{\scriptsize CISIR, Electrical \& Electronic Engineering Department, Universiti Teknologi Petronas, 32610 Seri Iskandar, Perak, Malaysia}
\cortext[cor1]{Corresponding author.}

% Start the abstract
\begin{abstract}
\Ac{mpmri} plays a major role in the detection of \ac{cap} and is commonly used to the design of new \ac{cad} systems.
\ac{dce}-\ac{mri} is one of the modality regularly used in \ac{mpmri} \ac{cad} system.
Pharmocokinetric parameters are extracted from the \ac{dce}-\ac{mri} sequences and later used to discriminate cancerous from healthy tissue.
However, some inter-patients variations occur during the data acquisition leading to estimation errors of the pharmacokinetic parameters.
Therefore, we propose a fully automatic normalization method for \ac{dce}-\ac{mri} that reduces the inter-patient variability of the data.
The benefit and simplicity of our approach is shown by detecting cancerous voxel from healthy voxel using the normalized enhanced \ac{dce}-\ac{mri} signal and comparing with the state-of-the-art quantitative and semi-quantitative methods.
Additionally, we show that using this normalization approach in conjunction with the quantitative methods improves the classification performance of most of the models.
The best classification performance to detect \ac{cap} is obtained using the whole \ac{dce}-\ac{mri} normalized signal, reaching an \ac{auc} of $0.666\ (\pm 0.154)$ and outperforming the quantitative approaches.
\end{abstract}

% Give the different keywords
\begin{keyword}
\acs*{dce}-\acs*{mri}\sep prostate cancer\sep normalization\sep classification
\end{keyword}

\end{frontmatter}

% Reset all the acronyms
\acresetall
\linenumbers
% Include now the different files
\input{01_introduction/introduction}
\input{02_methods/methods}
\input{03_experiments/experiments}
\input{04_discussions/discussions}
\input{05_conclusions/conclusions}
\input{06_appendix/appendix}

% Include the bibliography
\section*{References}

\bibliography{00_files_system/literature}

\end{document}